---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rchitex

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/bdempe18/rchitex.svg?branch=master)](https://travis-ci.org/bdempe18/rchitex)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/bdempe18/rchitex?branch=master&svg=true)](https://ci.appveyor.com/project/bdempe18/rchitex)
<!-- badges: end -->


RCHITEX provides an extensive set of options allowing users to generate and output nicely formatted text tables wiles simultaneously outputting the equivalent Latex code to a provided path. rchitex is intended to bridge the gap between statistical exploration in R and article writing.


## Installation

You will be able to install the released version of rchitex from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("rchitex")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("bdempe18/rchitex")
```

Until development exceeds the experimental phase, the package will only be available on github.

## Usage  

Rchitex was designed to produce underlying Latex code for regression tables and summary statistics while also providing an informative text display in the console. Rchitex can also directly output Latex and html which can be formatted with knitr and RMarkdown. The `build` method allows for the construction of heavily customizable regression tables. The `describe` method similarly allows for the construction of descriptive statistics tables originating from either a data frame, matrix, matrix, or tibble. 

```{r ex1, eval=FALSE}
data('freeny')
mod <- lm(y ~ lag.quarterly.revenue + price.index + income.level + 
            market.potential, data = freeny)
mod2 <- lm(y ~ lag.quarterly.revenue + price.index + income.level, 
           data = freeny)

# regression table
b <- build(mod1, mod, md='latex')

# summary statistics
df <- data.frame("first" = c(4,5,6), "second" = c(7,5,3))
d <- describe(df, md='html')
```

A full Latex appendix can be generated from any number of rchitex and ggplot object. The `appendize` function will save each table/plot in an organized tree structure and generate an *appendix.tex* file which presents each table/plot on a separate page all under an Appendix section label. 

```{r ex2, eval=FALSE}
fp <- paste(getwd(), 'rchitEx', sep='/')
appendize(b, d, dir=fp)
```

## Tutorial

A full tutorial of all features and available customization is available in the Usage vignette that comes with the package.
